% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2012 Josh Rendek josh@bluescripts.net> http://bluescripts.net/
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[a4paper,11pt,sans]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{myblue}{RGB}{52,107,166}
%52	107	166

\hypersetup{
    colorlinks=true,
    colorlinks=blue,
    urlcolor=blue
}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{myblue}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\def\doubleline{

    \vspace{-0.9em}
    \hspace{\fill}\line(1,0){500}\hspace{\fill}

    \vspace{-2em}
    \hspace{\fill}\line(1,0){500}\hspace{\fill}

}


%-----------------------------------------------------------


\begin{document}

\newcommand{\infoheader}{
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\LARGE Josh Rendek }  & 407-766-3134 (cell) \\
\href{mailto:josh@joshrendek.com}{\nolinkurl{josh@joshrendek.com}} & \url{https://github.com/joshrendek} \\
\url{http://joshrendek.com/} & \url{http://bitbucket.org/joshrendek} \\
\end{tabular*}
\\

\vspace{0.1in}
}

\newcommand{\pagebreakwithheader}{\pagebreak\infoheader}

\infoheader

\resheading{\color{white} Introduction}
\hspace{3pt} \\
I am a full stack developer with a passion for learning new things, especially security related. I tend to focus on automation over manual (builds, deployments, etc)
and favor picking the right tool for the job over being evangelical about one language.
\linebreak

\resheading{\color{white} Skills}

\begin{description}
    \item[Languages:] \hfill \\
        | Golang \textit{(2014-present)}
        | React \textit{(2014-present)}
        | Ruby/Rails \textit{(2008-Present)}
        | JRuby \textit{(2012-2014)}
        | Java (focus on Android) \textit{(1.5 Years)}
        | Scala \textit{(2014)}
        | HTML, CSS, JavaScript \textit{(2005-Present)}
        | C \textit{(2 Years)}
        | Python \textit{(1.5 Years)}
        | PHP \textit{(2007-2011,2015)}
    \item[Databases/Queues:] \hfill  \\
        | PostgreSQL \textit{(2013-Present)}
        | MySQL \textit{(2006-Present)}
        | MongoDB \textit{(2011-2013)}
        | ElasticSearch \textit{(2012-Present)}
        | Redis/Memcached \textit{(2011-Present)}
        | RabbitMQ \textit{(2014-Present)}
    \item[Operating Systems/Virtualization:] \hfill \\
        | Docker (2014-Present)
        | KVM
        | VirtualBox
        | Mac OSX
        | Debian-based distros \textit{(Debian/Ubuntu/Mint)}
        | Redhat-based distros \textit{(CentOS/RHEL/OEL)}
        | Windows XP, 7, 10
        | FreeBSD 5-7, 10
    \item[Other:] \hfill \\
        | AWS (EC2, ASG, ELB, RDS, EC, S3, CF, EB, Launch Configs, VPC, ECS, Route53, IAM, SES, SNS) \textit{(2012-Present)}
        | Ansible \textit{(2013-Present)}
        | InfluxDB
        | StatsD
        | Logstash
        | Kibana
        | Grafana
        | Torquebox
        | Rspec
        | Sinatra
        | Chef (2012-Present)
        | Zabbix (2012-Present)
        | Emacs
        | Vim
        | Git
        | nginx
        | unicorn
        | LigHTTPd
        | Puma
        | mongrel
        | thin
        | Apache
        | SendMail
        | Postfix
        | Dovecot
        | OpenVPN
        | SpamAssasin

\end{description}

\resheading{\color{white} Work Experience}

\ressubheading{Security Scorecard}{Remote}{Lead DevOps Engineer}{June 2015-Present}

\hspace{5pt} \\

Moved all servers to use Ansible as configuration management. Worked to find and build a hybrid solution (mix of dedicated / AWS) for our infrastructure. Heavy focus on performance optimizations with Go-lang and security tools like nmap, took lead on building out different tools and automation using Go. Built from the ground up a (Shodan-like) tool to scan the entire internet using masscan and nmap. Setup monitoring stack using Grafana, StatsD, InfluxDB for application metrics, Zabbix for alerting and server monitoring, and the ELK stack for log aggregation. Wrote tooling and libraries in Go to clean up projects, helped educate others on Go best practices. Migrated disparate server environments and one-off-tools to Docker and deployed via Jenkins/Ansible. Setup build environment and automation for all projects using Jenkins, Docker, and Ansible, including security and auditing tools to run on every build to check for vulnerabilities.

\hspace{5pt} \\

\ressubheading{Articulate, Inc.}{Remote}{Software Engineer \& DevOps}{April 2014-June 2015}

\hspace{5pt} \\

Gave talks on topics like microservices, Golang, and using Docker. Focus on code quality and meeting deliverables using Ruby, Rails, Coffeescript, React, Golang. Focus on backend development and breaking out into microservices where possible. Co-ordinated a lot of cross-team efforts to get parts of the product integrated. Assisted with build issues when they arose (Jenkins). Focused on delivering an MVP and minimizing scope creep.

\hspace{5pt} \\

\ressubheading{SysWard}{Remote}{Founder}{2014-Present}

\hspace{5pt} \\

Started a multi-operating system patch management SaaS that covered security alerting for Ubuntu, Debian, CentOS, Redhat, and other operating systems. Performance critical portions were written in Golang. Wrote several tools to manage Docker environments and deploy to AWS. Front-end made with ReactJS. \url{https://sysward.com/}

\hspace{5pt} \\

\ressubheading{ThreatTrack Security (formerly a part of GFI Software)}{Clearwater, FL \& Remote}{Software Engineer \& DevOps}{June 2012-April 2014}

\hspace{5pt} \\
Implemented and gave presentations on the usage and reasons to use Chef for configuration management. Strong focus on monitoring and root cause analysis in addition to capacity planning. Continued to create and improve documentation for systems. Created a
LISP-like lexer to translate from S-Expression into ElasticSearch query syntax. Heavy focus on JRuby and end-user deployment with automation and testing. Mostly used Ruby, also used Java and C\#
depending on the problem being solved. Researched various malware analysis tools and how to use them. Focused on TDD and automation for development tasks to minimize regressions.

\begin{center}
  \line(1,0){250}
\end{center}


\ressubheading{Department of Management Services, State of Florida}{Tallahassee, FL}{Software Engineer \& Systems Configuration, Applications Programmer III}{October 2011 - July 2012}

\hspace{5pt} \\

Promoted a better environment for testing and documentation. Migrated software stacks from Solaris/Apache/Passenger to CentOS/Nginx/Unicorn and REE to 1.9.3.
Re-designed the UI of several applications using Bootstrap. Promoted the use of JIRA and Github for issue and source control. Mixed Rails 3 and 2 environment.

\begin{center}
  \line(1,0){250}
\end{center}

\ressubheading{BlueScripts L.L.C.}{Remote}{Owner}{2008-Present (Incorporated 2011)}

\setlength{\parindent}{15pt}

\hspace{5pt} \\

Scrapes the FSU course list and allows a student to plan their semester with their friends. Integrates with Facebook and the ISBN db for book purchases.
Source available: \url{https://github.com/joshrendek/classopoly/}

\subparagraph{FSU Department of Psychology} \hspace{5pt} \\

Android tablet application that allowed a user to upload images and then draw on an overlay to track movement through the parking lot.

\subparagraph{Servly.com} \hspace{5pt} \\

Server monitoring application written in Ruby on Rails, eventually open sourced and ported to JRuby.

\subparagraph{NotecardApp.com} \hspace{5pt} \\

A simple notecard application that integrated with facebook for creating flashcards.

\setlength{\parindent}{0pt}

\begin{center}
  \line(1,0){250}
\end{center}


\ressubheading{\href{http://orlandophil.org/}{Orlando Philharmonic Orchestra}}{Remote}{Software Consultant}{August, 2009 - 2015}

\hspace{5pt} \\

Developed and maintained a shopping cart in Rails 2.3 with a focus on user experience. Configured and maintained Wordpress installation.


\begin{center}
  \line(1,0){250}
\end{center}


\ressubheading{BlueLite L.L.C.}{Remote}{Software \& Systems Engineer, Vice President}{2010 - October, 2011}

\hspace{5pt} \\

Created a billing system in Rails 3 for software management and purchasing with integration to Authorize.net CIM.
Setup and maintenance of various linux servers and test environments.


\begin{center}
  \line(1,0){250}
\end{center}

\ressubheading{Underground Tournaments L.L.C.}{Remote}{Software \& Systems Engineer, Partner}{2005 - October, 2011}

\hspace{5pt} \\

Created a client/server communications sytem in PHP to manage Ventrilo services.
Created a custom billing solution that integrated with PayPal and Authorize.net.
Created a custom server monitoring solution.
Maintained and setup FreeBSD 5.x-7.x and CentOS servers.
Created the client and adminstration user interfaces and graphics.
Helped answer cusomer support.
Used MySQL as the backend for all services.
Created a reseller system with a Ruby on Rails backend and a PHP front end.
Created a refresh of the billing system in Ruby on Rails.
Managed over 20 servers across the country and diagnosed and analyzed network and performance issues.

\begin{center}
  \line(1,0){250}
\end{center}


\ressubheading{MyGuildHost L.L.C.}{Remote}{Software \& Systems Engineer}{2008 - October, 2011}

\hspace{5pt} \\

Designed the sales website, several templates, and the administration interface.
Created a custom content management system with a focus on the gaming community.
Integrated with UltraDNS for managing server distribution.

\begin{center}
  \line(1,0){250}
\end{center}

\end{document}
